Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-14 paper.tex
Figure text wrapping
Fix up conclusion

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{figures/meancontquiv_10}
\caption{Mean velocity field at $x/D=1$, $\lambda=1.9$, and $Re_D=1.0 \times 10^6$.}
\label{fig:meancontquiv}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.8\textwidth]{figures/k_contours_10}
\caption{Turbulence kinetic energy at $x/D=1$, $\lambda=1.9$, and
$Re_D=1.0 \times 10^6$.}
\label{fig:kcont}
\end{figure}

@@

In this study it was demonstrated that the performance of a high solidity
($c/R=0.28$) cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
approximate Reynolds number based on blade chord of $Re_c \approx 2 \times
10^5$.

These results suggest that to validate predictive engineering models, one must
use data of at least this scale, especially for validation of high-fidelity CFD
models, where transition to turbulence may be completely different between
scaled physical model and full-scale prototype.

@@

If using scaled physical models to predict array performance, it is important to
keep all turbines in the regime where the power coefficient varies linearly to
avoid exaggerated power deficiencies for downstream turbines, despite
similarities in wake characteristics. These results also suggest that low
Reynolds number physical model studies of turbine arrays may see exaggerated
levels of wake recovery, leading to inadequate or inappropriate spacing or
layouts.

>>>>

\includegraphics[width=0.8\textwidth]{figures/meancontquiv_10}

\caption{Mean velocity field at $x/D=1$, $\lambda=1.9$, and $Re_D=1.0 \times
    10^6$.}

\label{fig:meancontquiv}
\end{figure}

\includegraphics[width=0.8\textwidth]{figures/k_contours_10}

\caption{Turbulence kinetic energy at $x/D=1$, $\lambda=1.9$, and $Re_D=1.0
    \times 10^6$.}

\label{fig:kcont}
\end{figure}

@@

In this study it was demonstrated that the performance of a high solidity
($c/R=0.28$) cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
approximate Reynolds number based on blade chord of $Re_c \approx 2 \times
10^5$. The left side of the $C_P$--$\lambda$ curve is further diminished at low
$Re$ due to deeper stalling. The $Re$-independent threshold corresponds to that
at which the foil suction surface boundary layer becomes turbulent before having
to recover static pressure against the adverse pressure gradient, highlighted in
\cite{Lissaman1983, McMasters1980, Carmichael1981}.

@@

At lower Reynolds numbers we observed lower levels of turbulence in the wake at
$x/D=1$, along with lower levels of turbulent transport with respect to mean
streamwise momentum and mean kinetic energy recovery in the streamwise
direction. Vertical advection---the largest transport mechanism
measured---showed little $Re$-dependence, whereas the negative effects of
cross-stream advection was enhanced at high $Re$. Despite being order of
magnitude smaller than other transport processes, viscous diffusion increased
rapidly with decreasing $Re$. Overall, the total wake transport measured leveled
off at essentially the same Reynolds number that the performance did.

From these results we can make the recommendation that physical model tests be
on the order $Re_D \sim 10^6$ to provide predictions of full-scale performance.
This threshold also applies to the validation of predictive engineering models,
especially for high-fidelity CFD models, where the boundary layer is to be
resolved, since transition to turbulence plays an important role in overall
blade loading.

If using scaled physical models to predict array performance, where turbine
power output is measured, it may also be important to keep all turbines in the
regime where the power coefficient varies linearly to avoid exaggerated power
deficiencies for downstream turbines, despite similarities in wake
characteristics. Results here also suggest that low Reynolds number physical
model studies of turbine arrays may see exaggerated levels of wake recovery,
leading to inadequate or inappropriate spacing or layouts.
